Flabby and injective objects in toposes

### 2022-04-04 paper-flabby-objects.tex
typo

>>>>

\begin{ex}The object of Dedekind reals of a topos is in general not flabby. For
instance, in the case of the topos of sheaves over the real line~$\mathbb{R}^1$, the
object of Dedekind reals is the sheaf~$\mathcal{C}$ of continuous (Dedekind-)real valued
functions~\XXX{cite}. The section~$1/x$ cannot be extended to opens containing
the origin.\end{ex}
